---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

# altqplot

This package is at the moment just a placeholder for one function, `alt_qplot`. Perhaps more functionality will get added, or this function will move elsewhere, or this package will continue as is... 

The goal of `alt_qplot` is to provide `qplot` like functionality for the [altair](https://github.com/vegawidget/altair) R package (which is a port of the [Altair python package](https://altair-viz.github.io/index.html)). Although altair (like `ggplot`) is very powerful thanks to the grammar of graphics framework, sometimes you want to very quickly make a plot and it is handy to be able to call one simple function. The purpose of the `alt_qplot` function in this package is to provide a convenient wrapper for quickly making a plot using altair. That plot can further be modified using altair methods, although when making anything beyond very simple plots, using altair directly should be preferred...

## Examples

```{r hist}
library(altqplot)
alt_qplot(x = mtcars$mpg)
```



```{r scatter}
alt_qplot(x = wt, y = mpg, data = mtcars)
```



You can also pass the encoding as strings. When doing so, you can specify the type (rather than altair picking its default):

```{r string}
alt_qplot(x = "wt", y = "mpg", color = "gear:N", data = mtcars)
```

You can also pass along altair's long form encoding:

```{r longform}
alt_qplot(x = alt$X("wt:Q", bin = TRUE), 
          y = alt$X("mpg:Q", bin = TRUE), 
          size = "count()", 
          data = mtcars)
```


# Future work

It might be useful to add a few more options to the `alt_qplot` function, such as facetting, although the goal is for this function to be pretty limited (b/c if you want something more complex you should use altair itself).   

Maybe a Python version of this function/package? (although in python a simpler interface to vegalite already exists through pdvega, and all the nse nonsense in this function doesn't really have python equivalents afaik)




